Self Regulation Ontology Retest Data Report

### 2018-01-25 code/SRO_Report.Rmd
going through rest of report with new releases

```{r}
#read t1 data
t1_hr = read.csv(gzfile('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Complete_01-15-2018/Individual_Measures/hierarchical_rule.csv.gz', 'rt'))

t2_hr = read.csv(gzfile('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_11-27-2017//Individual_Measures/hierarchical_rule.csv.gz', 'rt'))

>>>>

```{r}
#read t1 data
t1_hr = read.csv(gzfile(paste0(test_data_path,'Individual_Measures/hierarchical_rule.csv.gz'), 'rt'))

t2_hr = read.csv(gzfile(paste0(retest_data_path,'Individual_Measures/hierarchical_rule.csv.gz'), 'rt'))
